### 2018-03-09 paper/abstractions.tex
Add draft of S3

\clearpage

@@

In this section we present the \emph{compute} and \emph{build} abstractions:
\begin{itemize}
    \item Compute represents build rules (in build systems) or formulas (in
    spreadsheets), and is completely isolated from the world of compilers, file
    systems, memories, caches, and all other complexities of real build systems.
    \item Build corresponds to the algorithm used for bringing a key-value store
    to a coherent state by running compute.
\end{itemize}

\begin{figure}
\begin{minted}{haskell}
type Compute c k v = @\std{forall}@ f. c f => (k -> f v) -> k -> Maybe (f v)
\end{minted}
\caption{Compute abstractions}\label{fig-compute}
\end{figure}

Consider abstractions in Fig.~\ref{fig-compute}.

@@

We now describe several types of build systems according to their constraint
on the functor \hs{f}.

>>>>

@@

This section presents purely functional abstractions for build systems that
allow us to express all the intricacies of build systems discussed in the
previous section~\S\ref{sec-background} and design complex build systems from
simple primitives. Specifically, we present the \emph{compute} and \emph{build}
abstractions:

\begin{minted}[xleftmargin=10pt]{haskell}
type Compute c k v = @\std{forall}@ f. c f => (k -> f v) -> k -> Maybe (f v)
type Build c i k v = Compute c k v -> k -> Maybe i -> Map k v -> (i, Map k v)
\end{minted}

\noindent
Compute represents build rules (in build systems) or formulas (in spreadsheets),
and is completely isolated from the world of compilers, file systems, memories,
caches, and all other complexities of real build systems. We explain the compute
type in~\S\ref{sec-compute}, and then discuss several noteworthy special cases:
functorial (\S\ref{sec-compute-functor}), applicative
(\S\ref{sec-compute-applicative}) and monadic (\S\ref{sec-compute-monad}) types
of compute.

Build corresponds to the algorithm used for bringing a key-value store to a
consistent state by recomputing dirty values in an appropriate order. We explain
the build type in~\S\ref{sec-build}, and then provide implementations for several
build systems in~\S\ref{sec-examples}.

\subsection{Compute}\label{sec-compute}

% \begin{figure}
% \begin{minted}{haskell}
% type Compute c k v = @\std{forall}@ f. c f => (k -> f v) -> k -> Maybe (f v)
% \end{minted}
% \caption{Compute abstractions}\label{fig-compute}
% \end{figure}
% Consider abstractions in Fig.~\ref{fig-compute}.

\subsection{Functorial compute}\label{sec-compute-functor}
\subsection{Applicative compute}\label{sec-compute-applicative}
\subsection{Monadic compute}\label{sec-compute-monad}

\subsection{Build}\label{sec-build}

@@
